Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2020-01-05 write_up/reviewer_response.tex

\documentclass[10pt]{letter}

\usepackage[margin=2.54cm, a4paper]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{lscape}
\usepackage{longtable}
\usepackage{hhline}
\usepackage{booktabs}

\signature{\vspace*{-1cm} 
	Paul Dolder \\ 
	Dr C\'oil\'in Minto\\ 
	Prof Jean-Marc Guarini \\
	Dr Jan Jaap Poos}
\address{Paul Dolder \\
	Marine and Freshwater Research Centre \\ 
	Galway-Mayo Institute of Technology \\ 
	Dublin Road \\ 
	Galway \\ 
	Ireland}

@@

\begin{document}

\begin{large}

\begin{letter}{Prof. Brian D. Fath \\ Department of Biological Sciences \\
		Towson University \\ 8000 York Road \\ Towson \\ Maryland 21252 \\ USA}
\opening{Dear Professor Fath,}

RE: Ms. No. ECOMOD-19-631 \\
\\
Thank you for your email of 5 December 2019 with the favourable 'minor
revisions` review of our manuscript submission. We have reviewed all the
comments made by the editor and the two reviewers and addressed them
accordingly. We thank the reviewers for a constructive review which undoubtedly
improves the manuscript and we found little reason to disagree with their
comments. A summary of our changes are presented overleaf.  \\

We look forward to hearing back positively on these changes, and publication of
the manuscript in Ecological Modelling. \\
\\

\closing{Yours Sincerely,}

\end{letter}

\end{large}

@@

		\hline
		\textbf{Results} &  \\
\\
Line 376: What does "Visualized using Gerritsen (2014)" mean? & This was poorly
worded. In hindsight, this should also been in the caption of Figure 5, where
we've now added: "The figure shows catch composition at each spatial unit
represented by a square pie chart of the four populations. The area of each
colour is proportionate to the weight of each population caught in that unit.
Figure produced with the R package 'mapplots' (Gerritsen et al 2014). \\

@@

\\
Line 397: Are these the same figures in Table 7? If so, just refer to the table
and summarize & Thanks, we agree this improves readability and the three final
paragraphs in section 4.2 have been revised accordingly. \\

@@

Line 416: This section is a little confusing and needs to be refined/streamlined. & \\
\\
Line 418: This paragraph should be in methods. But you did it for all
populations, right? Not just population 3? & That's correct, the closures
affected all populations but the closures were targeted to reduce fishing
mortality on population 3. We have clarified and moved to the methods section.

@@

also occurs to me that there is an opportunity to introduce the terminology
from your R package here to make it very clear to the people using your code
how the functions work together… this is only an idea though… or maybe a
similar figure could be included with the vignette. & We have changed to 'Recr'
to make clearer. Rather than change the schematic, we have included a short
example vignette demonstrating the use of the code - hoping that this will
increase accessibility and further uptake. \\

@@

\\
Figure 5: Do the colors indicate the dominant population in each cell? It is
hard to imagine that one would assume only the presence of specific population
in the cell? Or do I have the wrong idea about what the plot is showing? & Each
cell has the four colours in proportion of the weight of each population caught
(as a square pie chart) - we've clarified this in the figure caption. \\

@@

\\
Figure 6: Add what the different colors mean to the legend & This is already
included \\

@@

Figure 9: So the top two panels show spatial distribution for population 3?
That needs to be added to the legend. Also there should be a red box on the top
plot too. & The top two panels show the spatial distribution of the fishing
effort before (a) and after (b) the spatial closures, while the bottom (c)
shows the suitable habitat for the population. We've clarified in the figure
caption. \\

@@

Thank etc..

\begin{center}

\large

	\begin{longtable}{p{12cm} | p{12cm}}
%	\caption{Highly resolved spatiotemporal simulations for exploring mixed
%	fishery dynamics}
		\toprule
		Comment & Response \\
		\\
		\hline
		\\
	\textbf{General comments} &  \\
\\
		 How many species does the model simulate? The authors refer to
		 the issue of catching unwanted species (vulnerable or low
		 quota species) when available quota species is caught, and it
		 suggested me that populations of different species is modeled
		 at the same time. However, they  did not describe how many
		 species could be simulated in each simulation, only that four
		 populations were simulated. Does the populations simulated in
		 different simulations, or all of them are simulated
		 simultaneously? The results indicate that the four populations
		 were simulated in the same simulation. Please, clarify this in
		 the MM.  & Thanks, a good point and we now emphasis that the
		 framework allows the user to define as many species as
		 required. There will be some computational/memory cap but we
		 see no reasons why you could not include 10s or more. We chose
		 four to keep the analysis more tractable. All the populations
		 are part of the same system, irrespective of the number of
		 species included (though they do not interact, for example,
		 through predator-prey relationships).\\
\\
There are too many figures and they should be better edited. Why the name of
the row and columns are inside the graphics? The axes scales and the axes title
should be greater. I would also send the figure 2, 3 and 9 as supplementary
data.  & \\
\\
The legends of the supplementary figures should be more informative. In the
Figure S2, what the light gray spots are? Habitat preference? Are the squares
the spawning areas? In the figure S3, are each square a week?  & \\
\\
I am not native English, but the language seems good for me. However, I missed
several commas along the text that make the sentences too long and hard to
understand. I suggest a revision of this.  & \\

@@

		\hline

	\textbf{Small issues} &  \\
\\
Line 14 - 18: This phrase is too long and hard to understand. Please, rephrase
this in shorter sentences to clarify this idea. & \\
\\
Lines 20 - 43: These two paragraphs seem redundant.  & \\
\\
Line 68 - 72: The authors mentioned that the MixFishSim could be used to infer
if fisheries data are the real community structure. I suggest adding one or two
phrases to explain how the model could help in this. & We explain that as our
community structure is simulated and therefore known, by comparing our inferred
community structure from commercial catches with our known true structure we
can understand how biases introduced by using commercial fishing as a sample
effects our understanding. We believe this point is adequately covered as
currently written.\\
\\
Line 90. The authors presented the time-step of each module, except the
Recruitment dynamics. The recruitment dynamics probably follow the population
dynamic, but it would be interesting present this explicitly. & Recruitment
occurs along with other population dynamics, but only during defined periods
for each population. We've clarified by saying "Population dynamics operate on
a daily time-step \textit{(with recruitment occurring only during defined
	seasons for each population), while..}\\
\\
Line 282: How these population parameters were selected? Randomly? Using real
data? Or the authors only created them? & The demographics were defined by the
authors to broadly reflect a four-species assemblage found in a typical
demersal fishery. We have clarified by including the sentence:  "The population
demographics were defined to broadly represent three mobile low-medium value
groundfish species and one high value species with low mobility, with the
dynamics hypothetical but as you might expect to find in a typical demersal
fishery." \\ 
\\ 
Line 426: What does adapted means in this context? Exploring
new opened areas?
& Yes, we have clarified in the text that "the fisheries "adapted" to the
closures textit{by fishing new areas of high abundance to fish}\\
\\
Line 613: Do not use parenthesis inside of other parenthesis. & We have changed
to ", e.g." from "( e.g." to eliminate one set of parenthesis. \\
\\
Table 2 and table 3 are not cited in the text Citation of the supplementary
figures are out of order & This is now corrected with references inserted for
Table 2 and 3 and the supplementary figures reorded. \\
\\
Figure 3: Individual years ARE the light grey lines    & Thanks! Corrected. \\
\\
Figure 4. What do the purple spots represent? Describe these spots in the
capture & This has been clarified to be the revenue at each location (darker
the area, higher the revenue). \\
Figure 7. Add what " res"  means in the caption.  & Have clarified in the
legend text that it means "resolution" \\
\\
Figure 8. What F means? & Changed to read "Fishing mortality" \\
\\
		\bottomrule
	\end{longtable}

### 2020-01-05 write_up/Process_model.tex
Addressing reviewer comments

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Overview schematic  
\begin{figure}[!ht]
	\hspace{-4em}
\begin{tikzpicture}[%
    >=triangle 60,              % Nice arrows; your taste may be different
    start chain=going below,    % General flow is top-to-bottom
    node distance=8mm and 60mm, % Global setup of box spacing
    every join/.style={norm},   % Default linetype for connecting boxes
    scale=0.9,
    every node/.style={scale=0.8}]                 
    \label{fig:model}
    % ------------------------------------------------- 
% A few box styles 
% <on chain> *and* <on grid> reduce the need for manual relative
% positioning of nodes
\tikzset{
  base/.style={draw, on chain, on grid, align=center, minimum height=4ex},
  proc/.style={base, rectangle, text width=8em},
  test/.style={base, rectangle, text width=5em},
  term/.style={proc, rounded corners},
  % coord node style is used for placing corners of connecting lines
  coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
  % nmark node style is used for coordinate debugging marks
  nmark/.style={draw, cyan, circle, font={\sffamily\bfseries}},
  % -------------------------------------------------
  % Connector line styles for different parts of the diagram
  norm/.style={->, draw, lcnorm},
  free/.style={->, draw, lcfree},
  cong/.style={->, draw, lccong},
  it/.style={font={\small\itshape}}
}
% -------------------------------------------------
% Start by placing the nodes in the middle
\node [proc, densely dotted, it] (p0) {start};
% Use join to connect a node to the previous one 
\node [term, join, fill=lcnorm!25]      {Choose random location to fish};
\node [term, join, fill=lcfree!25] (p1){Sample catch};
\node [test, densely dotted] (t1) {if $(Rec)$};
\node [test, join, densely dotted] (t2) {if (Pop Movement)};
\node [test, join, densely dotted] (wk) {if (Pop Dynamics)};
\node [test, join, densely dotted] (t3) {if (Past Knowledge)};
\node [term, join, fill=lcnorm!25]  (p2) {Correlated Random Walk};
\node [term, join, fill=lcnorm!25]  (p3) {Choose new fishing location};
\node [proc, densely dotted, join, it] (p7) {end};

@@

% -------------------------------------------------
% A last flourish which breaks all the rules
\draw [->,purple, dotted, thick, shorten >=1mm]
  (p3.south) -- ++(5mm,-3mm)  -- ++(87mm,0mm) 
  |- node [black, near end, yshift=1.75em, it]
    {} ($(p1.north) + (0,0.3)$);
% -------------------------------------------------
\end{tikzpicture}
\caption{Schematic overview of the simulation model. Blue boxes indicate fleet
	dynamics processes, the green boxes population dynamics processes while
	the white boxes are the time steps at which processes occur; $t$ = tow,
	$tmax$ is the total number of tows; (Rec), (Pop Movement), (Pop
	Dynamics) logic gates for recruitment periods, population movement and
	population dynamics for each of the populations, (Past Knowledge) a
	switch whether to use a random (exploratory) or past knowledge
	(exploitation) fishing strategy.}
%%\label{fig:overview}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Overview schematic  
\begin{figure}[!ht]
	\hspace{-4em}
\begin{tikzpicture}[%
    >=triangle 60,              % Nice arrows; your taste may be different
    start chain=going below,    % General flow is top-to-bottom
    node distance=8mm and 60mm, % Global setup of box spacing
    every join/.style={norm},   % Default linetype for connecting boxes
    scale=0.9,
    every node/.style={scale=0.8}]                 
    \label{fig:model}
    % ------------------------------------------------- 
% A few box styles 
% <on chain> *and* <on grid> reduce the need for manual relative
% positioning of nodes
\tikzset{
  base/.style={draw, on chain, on grid, align=center, minimum height=4ex},
  proc/.style={base, rectangle, text width=8em},
  test/.style={base, rectangle, text width=5em},
  term/.style={proc, rounded corners},
  % coord node style is used for placing corners of connecting lines
  coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
  % nmark node style is used for coordinate debugging marks
  nmark/.style={draw, cyan, circle, font={\sffamily\bfseries}},
  % -------------------------------------------------
  % Connector line styles for different parts of the diagram
  norm/.style={->, draw, lcnorm},
  free/.style={->, draw, lcfree},
  cong/.style={->, draw, lccong},
  it/.style={font={\small\itshape}}
}
% -------------------------------------------------
% Start by placing the nodes in the middle
\node [proc, densely dotted, it] (p0) {start};
% Use join to connect a node to the previous one 
\node [term, join, fill=lcnorm!25]      {Choose random location to fish};
\node [term, join, fill=lcfree!25] (p1){Sample catch};
\node [test, densely dotted] (t1) {if $(Recr)$};
\node [test, join, densely dotted] (t2) {if (Pop Movement)};
\node [test, join, densely dotted] (wk) {if (Pop Dynamics)};
\node [test, join, densely dotted] (t3) {if (Past Knowledge)};
\node [term, join, fill=lcnorm!25]  (p2) {Correlated Random Walk};
\node [term, join, fill=lcnorm!25]  (p3) {Choose new fishing location};
\node [proc, densely dotted, join, it] (p7) {end};

@@

% -------------------------------------------------
% A last flourish which breaks all the rules
\draw [->,purple, dotted, thick, shorten >=1mm]
  (p3.south) -- ++(5mm,-3mm)  -- ++(87mm,0mm) 
  |- node [black, near end, yshift=1.75em, it]
    {} ($(p1.north) + (0,0.3)$);
% -------------------------------------------------
\end{tikzpicture}
\caption{Schematic overview of the simulation model. Blue boxes indicate fleet
	dynamics processes, the green boxes population dynamics processes while
	the white boxes are the time steps at which processes occur; $t$ = tow,
	$tmax$ is the total number of tows; (Recr), (Pop Movement), (Pop
	Dynamics) logic gates for recruitment periods, population movement and
	population dynamics for each of the populations, (Past Knowledge) a
	switch whether to use a random (exploratory) or past knowledge
	(exploitation) fishing strategy.}
%%\label{fig:overview}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-01-05 write_up/mixfishsim_ecolmod_revisions.tex
Addressing reviewer comments

Population dynamics operate on a daily time-step, while population movement
occurs on a weekly time-step, with the fishing module operating on a tow-by-tow
basis (i.e.  multiple events a day).

@@

The basic population level processes were simulated using a modified two-stage
Deriso-Schnute delay difference model which models the fish populations in
terms of aggregate biomass of recruits and mature components rather than
keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}. A
daily time-step was chosen to discretise continuous population processes on a
biologically relevant and computationally tractable timescale. Population
biomass growth was modelled as a function of previous recruited biomass,
intrinsic population growth and recruitment functionally linked to the adult
population size.  Biomass for each cell $c$ was incremented each day $d$ as
follows (the full parameter list is detailed in Table \ref{tab: pop_variable}): 
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& \left(1 + \rho \right) B_{c,d} \cdot \mathrm{e}^{-Z_{c,d}} - \rho \cdot
	\mathrm{e}^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& \left(B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + Wt_{R-1} \cdot \left( \alpha_{d-1} \cdot
	R_{\tilde{y}(c)}\right) \right)
	\hspace{0.9cm} + \\
	& Wt_{R} \cdot \left( \alpha_{d} \cdot R_{\tilde{y}(c) \right)}
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be equal to $\mathrm{e}^{-K}$
when $K$ is the growth rate from a von Bertalanffy logistic growth model
\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y}(c)}$ is the annual recruits in year $y$ for cell $c$. \\

@@

A time-varying temperature covariate changes the interaction between time and
suitable habitat on a weekly time-step. Each population $p$ was assigned a
thermal tolerance with mean, $\mu_{p}$ and standard deviation, $\sigma_{p}$ so that
each cell and population temperature tolerance is defined that:
\begin{equation}
	Tol_{c, p, wk} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
		\frac{(T_{c, wk} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
\end{equation}
Where $Tol_{c, p, wk}$ is the tolerance of population $p$ for cell $c$ in week
$wk$, $T_{c, wk}$ is the temperature in the cell given the week and $\mu_{p}$
and $\sigma_{p}$ the mean and standard deviation of the population temperature
tolerance. \\

\deleted{The final combined process results in a population structure and movement
pattern unique to each population, with population movement occurring on a weekly
basis. The decision to model population movement on a weekly timescale was to
reflect that fish tend to aggregate in species specific locations that have
been observed to last around one to two weeks \citep{Poos2007}. Therefore this
process approximated the demographic shifts in fish populations throughout a
year with seasonal spawning patterns (Figure \ref{S-fig:5}).}

@@

For our implementation of a random walk directional change is based on a
negatively correlated circular distribution where a favourable fishing ground
is likely to be ``fished back over" by the vessel returning in the direction it
came from.  The step length (i.e. the distance travelled from the current to
the next fishing location) is determined by relating recent
fishing success, measured as the summed value of fish caught (revenue, $Rev$);
\begin{equation}
Rev_{c,d} = \sum_{p=1}^{P} L_{c,d,p} \cdot Pr_{p} 
\end{equation}
where $L_{c,d,p}$ is landings of a population $p$, and $Pr_{p}$ price of a
population. All population prices were kept the same across fleets and seasons.
Here, when fishing is successful vessels remain in a similar location and
continue to exploit the local fishing grounds. When unsuccessful, they move
some distance away from the current fishing location.  The movement distance
retains some degree of stochasticity, that can be controlled separately, but is
determined by the relationship: 
\begin{equation}
	Le = \mathrm{e}^{log(\beta_{1}) + log(\beta_{2}) -
		\left(log\left(\frac{\beta_{1}}{\beta_{3}}\right)\right) \cdot Rev
} 
\end{equation}
Where $\beta_{1}$, $\beta_{2}$ and $\beta_{3}$ are parameters determining the
shape of the step function in its relation to revenue, so that, a step from
($x_{t}$,$y_{t}$) to ($x_{t+1}$, $y_{t+1}$) is defined by:
\begin{equation}
	\begin{split}
 (x_{t+1}, y_{t+1}) =  & x_{t} + Le \cdot \cos \left(\frac{\pi \cdot
		 Br_{t+1}}{180}\right), \\ & y_{t} + Le \cdot \sin
 \left(\frac{\pi \cdot Br_{t+1}}{180}\right) \\	
 when  \hspace{0.5cm}     & Br_{t} < 180, Br_{t+1} = 180 + \sim vm[(0,360), k] \\
 			  & Br_{t} > 180, Br_{t+1} = 180 - \sim vm[(0,360), k] \\
	\end{split}
\end{equation}
where $Le$ is the step length, $Br_t$ is the bearing at time $t$, $k$ the
concentration parameter from the von Mises distribution that we correlate with
the revenue so that $k = (Rev + 1 / RefRev) \cdot max_{k}$, where $max_{k}$ is
the maximum concentration value, $k$, and $RefRev$ is parametrised as for
$\beta_{3}$ in the step length function.

@@

We calibrated the simulation model for four example populations with
different demographics, growth rates, natural mortality and recruitment
(Table \ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and
temperature (Figures \ref{S-fig:3}, with temperature tolerance \ref{S-fig:4})
defined to be unique to each population resulting in differently weekly
distribution patterns (Figures \ref{S-fig:5}-\ref{S-fig:7}). In addition, each
of the populations was assumed to have two defined spawning areas that result
in the populations moving towards these areas in pre-defined weeks (Figure
\ref{S-fig:2}) with population-specific movement rates (Table \ref{tab:1}).

@@

We allow the simulation to run unrestricted for 30 years, then implement
spatial closed areas for the last 20 years of the simulation based on data
(either derived from the commercial catches, fisheries-independent survey or
the true population used at different spatial and temporal scales. \\

@@

Survey closures were on an annual basis only, as this was the most temporally
resolved survey data available. We evaluated the factors contributing to the
success of the closures through a regression tree (using the R package REEMtree
\citep{Sela2012}) to identify the factor most contributing to differences in
fishing mortality before and after the closure.

@@

Different perceptions of the proportion of each stock in an area are seen when
we aggregate the data over a smaller geographical region at different
timescales, with weekly (top), monthly (middle) and yearly (bottom) catch
compositions from across an aggregated 20 x 20 area (Figure \ref{fig:2}). In
the true population, the monthly aggregation captures the major patterns of
composition seen in the weekly data with the percentage of different
populations in the catch having similar mean and standard deviations.  In the
weekly data population 1 = 9.36\% (SD = 3.99), population 2 = 83.2\% (5.60),
population 3 = 3.57\% (1.23), population 4 = 3.91\% (1.59); in the monthly data
population 1 = 9.23\% (3.87), population 2\% = 83.3 (5.52), population 3 =
3.62\% (1.15), population 4 = \deleted{\%}3.86\added{\%} (1.52). While means
were similar some of the variation was lost when aggregated to an annual level;
population 1 = 9.90\% (0.173), population 2 = 82.2\% (0.308), population 3 =
3.82\% (0.119), population 4 = 4.03\% (0.0502).\\

The commercial data on a weekly basis shows some of the same patterns as the
true population, though the population 1 \deleted{(in red)} is less well
represented and some weeks are missing catches from the area. Here, weekly and
monthly compositions were nearly identical, with monthly composition of
population 1 = 0.0472\% (0.0139), population 2 = 94.4\% (1.47), population 3 =
3.12\% (1.47), population 4 = 2.40\% (0.444). \deleted{Again, y}\added{Y}early
values head a similar mean but smaller standard deviation.\\

The survey data was only available on an annual basis, and showed again a
slightly different composition; population 1 = 0.372\% (0.00473), population 2
= 87.7\% (0.193), population 3 = 0.729\% (0.0200), population 4 = 11.2\%
(0.172).

@@

We implemented a spatial closure using the different data sources and spatial
and temporal aggregations as outlined in the protocol in Section 3.4. We used
this to assess the efficacy of a closure in reducing fishing mortality on
population 3, given availability of data and its use at different resolutions in
order to evaluate the trade-offs in data sources.

In most cases the fishery closure was successful in reducing fishing mortality
on the species of interest (population 3; Figure \ref{fig:3}), though
interestingly the largest reductions in fishing mortality happened immediately
after the closures, following which the fisheries ``adapted" to the closures
and fishing mortality increased again somewhat. The exception to the success
was the closures implemented based on the coarsest spatial (20 x 20) and
temporal resolution (yearly) that was ineffective (i.e. failed to reduce
fishing mortality) with all data sources. As expected, closures based on the
``known" population distribution were most effective, with differing degrees of
success using the commercial data. Fishing mortality rates on the other species
changed in different proportions, depending on whether the displaced fishing
effort moved to areas where the populations were found in greater or lesser
density. \\

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/Combined_Movement}
	\caption{(A) The fishing locations (points) and movements (lines) of a
		single vessel during a trip overlaid on the revenue of a
		fishing site (landings x price); (B) the fishing locations of
		the vessel over several trips (value field changes over the
		period so not shown). Note that movements are a mixture of
		correlated random walk (solid lines) and experience-based
		(dashed lines), and that the field is wrapped on a torus so
		that opposite sides of the spatial domain are considered
		spatially close; (C) the locations of multiple vessels from the
		same fleet overlaid on the value field, (D) the realised step
		distance and turning angles for a single vessel over the
		simulation.}
	\label{fig:mv}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev2}
	\caption{[Colour] Data aggregation at different spatial resolutions over a
		ten year period. The figure shows catch composition at each
		spatial unit as visualised using \cite{Gerritsen2014} mapplots
		R package.}
	\label{fig:1}
\end{figure}

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width =0.5\linewidth]{./Plots/Closure_fishing_locations_yearly}
	\caption{Closure fishing locations based on annual closures with a
		coarse spatial resolution. Closure location can be seen in red
		box in relation to a) before the closure fishing locations, b)
		after the closure fishing locations, c) population 3 habitat
		distribution.}
	\label{fig:17}
\end{figure}

>>>>

Population dynamics \added{for any number of species, as chosen by the user}
operate on a daily time-step \added{(with recruitment occurring only during
	defined seasons for each population)}, while population movement occurs
on a weekly time-step, with the fishing module operating on a tow-by-tow basis
(i.e.  multiple events a day). \\

@@

The basic population level processes were simulated using a modified two-stage
Deriso-Schnute delay difference model which models the fish populations in
terms of aggregate biomass of recruits and mature components rather than
keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}. A
daily time-step was chosen to discretise continuous population processes on a
biologically relevant and computationally tractable timescale. Population
biomass growth was modelled as a function of previous recruited biomass,
intrinsic population growth and recruitment functionally linked to the adult
population size.  Biomass for each cell $c$ was incremented each day $d$ as
follows (the full parameter list is detailed in Table \ref{tab: pop_variable}): 
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& \left(1 + \rho \right) B_{c,d} \cdot \mathrm{e}^{-Z_{c,d}} - \rho \cdot
	\mathrm{e}^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& \left(B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + Wt_{R-1} \cdot \left( \alpha_{d-1} \cdot
	R_{\tilde{y}\left(c\right)}\right) \right)
	\hspace{0.9cm} + \\
	& Wt_{R} \cdot \left( \alpha_{d} \cdot R_{\tilde{y} \left(c\right)}
	\right) \\
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be equal to $\mathrm{e}^{-K}$
when $K$ is the growth rate from a von Bertalanffy logistic growth model
\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y}(c)}$ is the annual recruits in year $y$ for cell $c$. \\

@@

A time-varying temperature covariate changes the interaction between time and
suitable habitat on a weekly time-step. Each population $p$ was assigned a
thermal tolerance with mean, $\mu_{p}$ and standard deviation, $\sigma_{p}$ so that
each cell and population temperature tolerance is defined that:
\begin{equation}
	Tol_{c, p, wk} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
		\frac{(T_{c, wk} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
\end{equation}
Where $Tol_{c, p, wk}$ is the tolerance of population $p$ for cell $c$ in week
$wk$, $T_{c, wk}$ is the temperature in the cell given the week and $\mu_{p}$
and $\sigma_{p}$ the mean and standard deviation of the population temperature
tolerance. The variables, their meaning and units for population movement is
provided in Table \ref{tab:pop_move}. \\

\deleted{The final combined process results in a population structure and movement
pattern unique to each population, with population movement occurring on a weekly
basis. The decision to model population movement on a weekly timescale was to
reflect that fish tend to aggregate in species specific locations that have
been observed to last around one to two weeks (Poos et al 2007). Therefore this
process approximated the demographic shifts in fish populations throughout a
year with seasonal spawning patterns (Figure \ref{S-fig:5}).}

@@

For our implementation of a random walk directional change is based on a
negatively correlated circular distribution where a favourable fishing ground
is likely to be ``fished back over" by the vessel returning in the direction it
came from.  The step length (i.e. the distance travelled from the current to
the next fishing location) is determined by relating recent
fishing success, measured as the summed value of fish caught (revenue, $Rev$);
\begin{equation}
Rev_{c,d} = \sum_{p=1}^{P} L_{c,d,p} \cdot Pr_{p} 
\end{equation}
where $L_{c,d,p}$ is landings of a population $p$, and $Pr_{p}$ price of a
population. All population prices were kept the same across fleets and seasons.
Here, when fishing is successful vessels remain in a similar location and
continue to exploit the local fishing grounds. When unsuccessful, they move
some distance away from the current fishing location.  The movement distance
retains some degree of stochasticity, that can be controlled separately, but is
determined by the relationship: 
\begin{equation}
	Le = \mathrm{e}^{log(\beta_{1}) + log(\beta_{2}) -
		\left(log\left(\frac{\beta_{1}}{\beta_{3}}\right)\right) \cdot Rev
} 
\end{equation}
Where $\beta_{1}$, $\beta_{2}$ and $\beta_{3}$ are parameters determining the
shape of the step function in its relation to revenue, so that, a step from
($x_{t}$,$y_{t}$) to ($x_{t+1}$, $y_{t+1}$) is defined by:
\begin{equation}
	\begin{split}
 (x_{t+1}, y_{t+1}) =  & x_{t} + Le \cdot \cos \left(\frac{\pi \cdot
		 Br_{t+1}}{180}\right), \\ & y_{t} + Le \cdot \sin
 \left(\frac{\pi \cdot Br_{t+1}}{180}\right) \\	
 when  \hspace{0.5cm}     & Br_{t} < 180, Br_{t+1} = 180 + \sim vm[(0,360), k] \\
 			  & Br_{t} > 180, Br_{t+1} = 180 - \sim vm[(0,360), k] \\
	\end{split}
\end{equation}
where $Le$ is the step length, $Br_t$ is the bearing at time $t$, $k$ the
concentration parameter from the von Mises distribution that we correlate with
the revenue so that $k = (Rev + 1 / RefRev) \cdot max_{k}$, where $max_{k}$ is
the maximum concentration value, $k$, and $RefRev$ is parametrised as for
$\beta_{3}$ in the step length function. Details of the variables, meaning and
units for fleet dynamics are provided in Table \ref{tab:fleet_dyn}.

@@

We calibrated the simulation model for four example populations with different
demographics, growth rates, natural mortality and recruitment (Table
\ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and temperature
(Figures \ref{S-fig:3}, with temperature tolerance \ref{S-fig:4}) defined to be
unique to each population resulting in differently weekly distribution patterns
(Figures \ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations was
assumed to have two defined spawning areas that result in the populations
moving towards these areas in pre-defined weeks (Figure \ref{S-fig:2}) with
population-specific movement rates (Table \ref{tab:1}).  \added{The population
demographics were defined to broadly represent three mobile low-medium value
groundfish species and one high value species with low mobility, with the
dynamics hypothetical but as you might expect to find in a typical demersal
fishery.}

@@

We allow the simulation to run unrestricted for 30 years, then implement
spatial closed areas for the last 20 years of the simulation based on data
(either derived from the commercial catches, fisheries-independent survey or
the true population) used at different spatial and temporal scales. \\

@@

\added{We implemented a series of spatial closures targeted at reducing fishing
	mortality on population 3, given the different data sources and spatial
	and temporal resolutions above. We use the effectiveness of these
	closures in reducing fishing mortality as a way of evaluating the
	trade-offs in data sources and resolution.} Survey closures were on an
annual basis only, as this was the most temporally resolved survey data
available. We evaluated the factors contributing to the success of the closures
through a regression tree (using the R package REEMtree \citep{Sela2012}) to
identify the factor most contributing to differences in fishing mortality
before and after the closure.

@@

Different perceptions of the proportion of each stock in an area are seen when
we aggregate the data at different timescales, with weekly (top), monthly
(middle) and yearly (bottom) catch compositions from across an aggregated 20 x
20 area showing different patterns (Figure \ref{fig:2}). In the true
population, the monthly aggregation captures the major patterns of composition
seen in the weekly data with the percentage of different populations in the
catch having similar mean and standard deviations (Table \ref{tab:7}). In the
weekly and monthly data population 2 dominates. However, some of the variation
was lost when aggregated to an annual level, as indicated from the lower
standard deviations (Table \ref{tab:7}).\\

The commercial data on a weekly basis shows some of the same patterns as the
true population, though the population 1 \deleted{(in red)} is less well
represented and some weeks are missing catches from the area. Here, weekly and
monthly compositions were nearly identical (Figure \ref{fig:2}; Table
\ref{tab:7}). \deleted{Again, y}\added{Y}early values head a similar mean but
smaller standard deviation.\\

The survey data was only available on an annual basis, and showed again a
slightly different composition from the true population and the commercial
data; in particular a greater proportion of population 4 (Figure \ref{fig:2}).

@@

\deleted{We implemented a spatial closure using the different data sources and
	spatial and temporal aggregations as outlined in the protocol in
	Section 3.4. We used this to assess the efficacy of a closure in
	reducing fishing mortality on population 3, given availability of data
	and its use at different resolutions in order to evaluate the
	trade-offs in data sources. }

In most cases the fishery closure was successful in reducing fishing mortality
on the species of interest (population 3; Figure \ref{fig:3}), though
interestingly the largest reductions in fishing mortality happened immediately
after the closures, following which the fisheries ``adapted" to the closures
\added{by finding new areas of high abundance to fish} and fishing mortality
increased again somewhat. The exception to the success was the closures
implemented based on the coarsest spatial (20 x 20) and temporal resolution
(yearly) that was ineffective (i.e. failed to reduce fishing mortality) with
all data sources. As expected, closures based on the ``known" population
distribution were most effective, with differing degrees of success using the
commercial data. Fishing mortality rates on the other species changed in
different proportions, depending on whether the displaced fishing effort moved
to areas where the populations were found in greater or lesser density. \\

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/Combined_Movement}
	\caption{(A) The fishing locations (points) and movements (lines) of a
		single vessel during a trip overlaid on the revenue of a
		fishing site (landings x price; darker purple = higher
		revenue); (B) the fishing locations of the vessel over several
		trips (value field changes over the period so not shown). Note
		that movements are a mixture of correlated random walk (solid
		lines) and experience-based (dashed lines), and that the field
		is wrapped on a torus so that opposite sides of the spatial
		domain are considered spatially close; (C) the locations of
		multiple vessels from the same fleet overlaid on the value
		field, (D) the realised step distance and turning angles for a
		single vessel over the simulation.}
	\label{fig:mv}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev2}
	\caption{[Colour] Data aggregation at different spatial resolutions
		over a ten year period. \added{The figure shows catch
			composition at each spatial unit represented by a
			square pie chart of the four populations. The area of
			each colour is proportionate to the weight of each
			population caught in that unit. Figure produced using
			the R package 'mapplots' (\cite{Gerritsen2014}.}}
	\label{fig:1}
\end{figure}

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width =0.5\linewidth]{./Plots/Closure_fishing_locations_yearly}
	\caption{The location of fishing effort before the spatial closure (a)
		and after the spatial closure (b), and the suitable habitat for
		population 3 (c). The site of the closure can be seen in the
		red box on all three panels.}
	\label{fig:17}
\end{figure}
